A significance test for forward stepwise model selection

### 2014-10-08 biostatistics/paper.tex
Added diabetes example

The main result in \cite{tests:adaptive} shows that
$T\chi \sim \text{Unif}([0,1])$ under the global null. In forward stepwise
we iterate this test on the residual after each step, and show in simulations
that it performs well.

@@

>>>>

The main result in \cite{tests:adaptive} shows that
$T\chi \sim \text{Unif}([0,1])$ under the global null. In forward stepwise
we iterate this test on the residual after each step, and show in simulations
that it performs well. As a simple example, and for comparison to other methods using the same data, we apply our method on the diabetes dataset described in \cite{lars}. The outcome is a measurement of disease progression, and we regress this on baseline measurements of various health indicators. Table~\ref{tab:diabetes} shows a comparison between the $T\chi$ $p$-values and standard $\chi^2$ $p$-values.

@@

% latex table generated in R 3.1.0 by xtable 1.7-3 package
% Tue Oct  7 22:25:31 2014
\begin{table}[ht]
\centering
\begin{tabular}{r|rrrrrrrrr}
  \hline
Variable & bmi & ltg & map & hdl & sex & ldl & glu & tc & tch \\ 
  \hline
T$\chi$ $p$-value & 0.000 & 0.000 & 0.008 & 0.729 & 0.002 & 0.622 & 0.353 & 0.652 & 0.420 \\ 
$\chi^2$ $p$-value & 0.000 & 0.000 & 0.000 & 0.001 & 0.000 & 0.073 & 0.277 & 0.101 & 0.266 \\ 
   \hline
\end{tabular}
\caption{Forward stepwise results on diabetes dataset. Chi-squared $p$-values are computed using the drop in residual sum of squares. Variables are listed in the order of inclusion by forward stepwise.} 
\label{tab:diabetes}
\end{table}
